Predicting Probability of Participants' Vote of Conservative and Liberty in 2025 Canadian election 

### 2024-04-15 paper/paper(1).qmd
Add files via upload

### Data Summary Measures

```{r}
#| label: tbl-data-summary
#| tbl-cap: Summary of Numerical Variables Across Census and Survey Data
#| echo: false
numeric_summary_df <- data.frame(
  Variable = c("Age in Census Data", "Age in Survey Data", 
               "Liberal Votes in Survey", "Conservative Votes in Survey"),
  Minimum = c(15.0, 18.0, 0.000, 0.000),
  Q1 = c(37.0, 36.0, 0.000, 0.000),
  Median = c(54.0, 53.0, 0.000, 0.000),
  Average = c(52.18, 51.3, 0.267, 0.249),
  Q3 = c(67.0, 66.0, 1.000, 0.000),
  Maximum = c(80.0, 97.0, 1.000, 1.000)
)

knitr::kable(numeric_summary_df)
```

@@

Table2: Summary the residuals for Conservative Party:
```{r echo=FALSE, warning=FALSE}

@@

# Create a table of the data
kable(table_summary, caption = "Summary of Residuals by Party")

@@

Table3: Summary the coefficient for Liberal Party:

```{r echo=FALSE, warning=FALSE}

liberal_coefs <- coef(liberal_model)
conservative_coefs <- coef(conservative_model)

liberal_coefs_df <- data.frame(Estimate = liberal_coefs, row.names = NULL)
conservative_coefs_df <- data.frame(Estimate = conservative_coefs, row.names = NULL)

liberal_coefs_df$Term <- names(liberal_coefs)
conservative_coefs_df$Term <- names(conservative_coefs)

liberal_coefs_df <- liberal_coefs_df[, c("Term", "Estimate")]
conservative_coefs_df <- conservative_coefs_df[, c("Term", "Estimate")]

knitr::kable(liberal_coefs_df, caption = "Coefficients of the Liberal Model", row.names = FALSE)
knitr::kable(conservative_coefs_df, caption = "Coefficients of the Conservative Model", row.names = FALSE)

>>>>

### Data Summary Measures
```{r}
#| label: tbl-data-summary-numeric
#| tbl-cap: Summary of Numerical Variables Across Census and Survey Data
#| echo: false
numeric_summary_df <- data.frame(
  Variable = c("Age in Census Data", "Age in Survey Data", 
               "Liberal Votes in Survey", "Conservative Votes in Survey"),
  Minimum = c(15.0, 18.0, 0.000, 0.000),
  Q1 = c(37.0, 36.0, 0.000, 0.000),
  Median = c(54.0, 53.0, 0.000, 0.000),
  Average = c(52.18, 51.3, 0.267, 0.249),
  Q3 = c(67.0, 66.0, 1.000, 0.000),
  Maximum = c(80.0, 97.0, 1.000, 1.000)
)

knitr::kable(numeric_summary_df)

@@

Table2: Summary the residuals for Conservative Party:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-data-summary
#| tbl-cap: Summary of Numerical Variables Across Census and Survey Data
#| echo: false

@@

kable(table_summary, caption = "Summary of Residuals by Party")

```
@tbl-data-summary

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-coef-summary-liberal
#| tbl-cap: Coefficients of the Liberal Model
#| echo: false

liberal_coefs <- coef(liberal_model)
liberal_coefs_df <- data.frame(Estimate = liberal_coefs, row.names = NULL)
liberal_coefs_df$Term <- names(liberal_coefs)
liberal_coefs_df <- liberal_coefs_df[, c("Term", "Estimate")]
knitr::kable(liberal_coefs_df, row.names = FALSE)

```
@tbl-coef-summary-liberal

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: tbl-coef-summary-conservative
#| tbl-cap: Coefficients of the Conservative Model
#| echo: false

conservative_coefs <- coef(conservative_model)
conservative_coefs_df <- data.frame(Estimate = conservative_coefs, row.names = NULL)
conservative_coefs_df$Term <- names(conservative_coefs)
conservative_coefs_df <- conservative_coefs_df[, c("Term", "Estimate")]
knitr::kable(conservative_coefs_df, row.names = FALSE)

@@

@tbl-coef-summary-conservative
